Light Transport Techniques for Tensor Field Visualization

### 2019-08-13 beamer2thesis/dummy.tex
update

\frame{
\frametitle{{Transmission Profiles}}
{\small To interpret singular value systems of tensors as conductivity property for light transport, we will need transfer functions (transmission profiles) for the propagation scheme:}
\begin{block}{\centering \textbf{Ellipse Equation}}
\begin{align*}
	T(\omega) = \frac{ab}{\sqrt{a^{2}\sin^{2}(\omega-\varphi)+b^{2}\cos^{2}(\omega-\varphi)}} =\frac{\sigma_1\sigma_2}{\sqrt{\sigma_1^2\sin^2(\omega-\varphi)+\sigma_2^2\cos^2(\omega-\varphi)}}
\end{align*}
{\small with $\varphi=\mathop{atan2}(\sigma_{1,y},\sigma_{1,x})$ and $\sigma$: singular value, $a$: x-radius ellipse, $b$: y-radius ellipse}
\end{block}
$\Rightarrow$ transmission profiles $r(\omega)$ are defined as polar functions by the mapping of singular values to half-axes radii and the shift angle of the major singular vector $\varphi$

>>>>

\frame{
\frametitle{{Evaluation - Light Transport Gradient - Gyre Field}}
\begin{figure}[!t]
\centering
\caption*{\textit{Gyre test field}}\bigskip
  \begin{minipage}[t]{0.3\textwidth}
    \centering
  \includegraphics[height=0.7\textwidth]{img/gyre.png}
	{\scriptsize a)~Glyphs}
    \label{a)}
  \end{minipage}
  \begin{minipage}[t]{0.3\textwidth}
    \centering
    \includegraphics[height=0.7\textwidth]{gyre_ftle.PNG}
	{\scriptsize b)~LTG($0^\circ$)}
    \label{b)}
  \end{minipage}
  \begin{minipage}[t]{0.3\textwidth}
    \centering
    \includegraphics[height=0.7\textwidth]{gyre_ftle_org.PNG}
	{\scriptsize c)~}{\tiny T-FTLE: Hlawatsch's approach}
    \label{b)}
  \end{minipage}
\label{gyre-ftle}
\end{figure}
\bigskip
\begin{itemize}
	\item LTG is detecting ridges for diverging light distributions
	\item decreased response in gyre centers for circular overlap in difference image
\end{itemize}
} % END OF FRAME
